Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
capitalize refs to Supplement

Our lower bound $\lowerBound$ is unconventional,
and one might wonder why we do not instead maximize an ELBO-style bound like in a VAE or in the EM algorithm.
We explain in the supplement that maximizing an ELBO-style bound
leads to a pathological behavior that  causes the model to easily become trapped in local optima.

@@

The architecture of $q$ depends upon the domain.
For domains with sequential structure like strings and lists,
we use an RNN to encode each input/output example,
and for domains with fixed-dimensionality inputs/outputs we use a multilayer perceptron.
We MaxPool across all of the input/output examples. See supplement for details.

>>>>

Our lower bound $\lowerBound$ is unconventional,
and one might wonder why we do not instead maximize an ELBO-style bound like in a VAE or in the EM algorithm.
We explain in the Supplement that maximizing an ELBO-style bound
leads to a pathological behavior that  causes the model to easily become trapped in local optima.

@@

The architecture of $q$ depends upon the domain.
For domains with sequential structure like strings and lists,
we use an RNN to encode each input/output example,
and for domains with fixed-dimensionality inputs/outputs we use a multilayer perceptron.
We MaxPool across all of the input/output examples. See Supplement for details.
